Division and Factorization of p-Adic Polynomials

### 2016-01-08 polynomials/muldivfact.tex
Minor corrections
Typos, etc...

@@

It worths be noting that tracking precision using this representation is 
rather easy. For example, if $x$ and $y$ are known with absolute (resp. 
relative) precision $N_x$ and $N_y$ respectively, one can compute the 
sum $x+y$ (resp. the product $xy$) at absolute (resp. relative) 
precision $\min(N_x,N_y)$. Computations with $p$-adic and Laurent
series are often handle this way on symbolic computation softwares.

@@

\begin{deftn}
A \emph{Newton function of degree $n$} is a convex function 
$\varphi : [0,n] \to \R \cup \{+\infty\}$ which is piecewise affine, 
which takes a finite value at $n$ and whose epigraph $\Epi(\varphi)$ 
have integral extremal points.
\end{deftn}

@@

\todo{Add introduction.}
In the sequel, we shall will the notation $A \div B$ (resp $A \mod B$)
for the quotient (resp. the remainder) in the Euclidean division of $A$ 
by $B$.

@@

\noindent
{\bf Newton precision.}
We consider here the case where the precision is given by Newton
functions. Concretely, we pick $A, B \in K[X]$ two polynomials which 
are known at precision $O(\varphi_A)$ and $O(\varphi_B)$ respectively:
$$A = A_\app + O(\varphi_A)
\quad \text{and} \quad
B = B_\app + O(\varphi_B)$$
Here $A_\app$ and $B_\app$ are some approximations of $A$ and $B$ respectively 
and $\varphi_A$ and $\varphi_B$ denotes two Newton functions of degree 
$\deg A$ and $\deg B$ respectively.
We are interesting in determining the precision on $A \mod B$ and $A
\div B$. The following proposition gives a theoretical answer under
mild assumptions.

@@

We observe several interesting properties. First of all, the gains for 
Newton precision and jagged precision always agree though one may has 
thought at first that Newton precision is weaker. Since performing
precision computations in the Newton framework is cheaper, it seems
(at least on this example) that using the jagged precision model is not
relevant.

@@

\subsubsection{Tristan's proof}

@@

\subsubsection{Xavier's proof}

If $\lambda_0 = -\infty$ or $\lambda_1 = +\infty$, the sequence $(A_i)$
is constant and the theorem is obvious. We then assume that $\lambda_0$
and $\lambda_1$ are both finite.
We notice that, when the polynomial is changed into $cP$ where $c$ is a 
nonzero constant lying in a finite extension of $K$, the $A_i$'s are all 
multiplied by $c$ as well whereas the $B_i$'s and the $V_i$'s remained 
unchanged. Therefore, the theorem holds for $P$ if and only if it holds 
for $cP$. As a consequence we may assume that $P$ is normalized so that 
$\NF(P)(d) = d \lambda_0$. We define the function $\varphi : \R^+ \to \R 
\cup \{+\infty\}$ by:
\begin{equation}
\label{eqdef:functionphi}
\begin{array}{r@{\,\,}ll}
\varphi(x) & = \NP(P)(x) & \text{for } x \leq d \smallskip \\
& = \lambda_0 (x-d) + \NP(P)(d) & \text{for } x > d.
\end{array}
\end{equation}
For a polynomial $Q \in K[X]$ of degree $n$, we further define:
\begin{align}
b_\varphi(Q) & = \min_{x \in [0,n]} \NF(Q)(x) - \varphi(x) 
\label{eqdef:bphi} \\
\text{and} \quad
b_0(Q) & = \min_{x \in [0,n]} \NF(Q)(x) - \lambda_0 x.
\label{eqdef:b0}
\end{align}
Set also $b_\varphi(0) = b_0(0) = +\infty$ by convention.
With the normalization of $P$ we have chosen above, we have $b_0(P)
= b_\varphi(P) = 0$ and $b_\varphi(Q) \leq b_0(Q)$ for all polynomial
$Q$.

\begin{lem}
\label{lem:bphib0}
Let $b \in \{b_\varphi, b_0\}$. For $Q_1, Q_2 \in K[X]$:

@@

c) $b_\varphi(Q_1 Q_2) \geq b_\varphi(Q_1) + b_0(Q_2) \geq
b_\varphi(Q_1) + b_\varphi(Q_2)$

@@

Let $t_1$ (resp. $t_2$) be the translation of vector $(0, b_\varphi
(Q_1))$ (resp. $(0, b_0(Q_2))$. It follows from the definition of
$b_\varphi$ that $\NP(Q_1)$ is a subset of $t_1(\Epi(\varphi))$ where
$\Epi(\varphi)$ denotes the epigraph of $\varphi$. Similarly $\NP(Q_2)
\subset t_2(C)$ where $C$ is the convex cone generated by the vectors
$(0,1)$ and $(1, \lambda_0)$. Thus
$$\NP(Q) \subset t_2 \circ t_1 \big(\Epi(\varphi) + C\big) =
t_2 \circ t_1\big(\Epi(\varphi)\big)$$
and \emph{c)} follows.

@@

We are now going to prove by induction on $i$ the conjonction of all
equalities and inequalities below:
\begin{equation}
\label{eq:induction}
\begin{array}{l}
\NF(A_i) = \varphi_{|[0,d]}, \smallskip \\
b_0(V_i) \geq 0, \quad
b_\varphi(R_i) \geq 2^i \kappa \smallskip \\
b_\varphi(S_i) \geq 0, \quad
b_0(T_i) \geq 2^i \kappa.
\end{array}
\end{equation}

Noting that $A_0$ and $P$ agree up to degree $d$ and that $\NP(P)$ has 
an extremal point at abscissa $d$, we get $\NF(A_0) = \varphi_{|[0,d]}$.
Clearly $b_0(V_0) \geq 0$ since $V_0 = 1$. It follows from the 
definitions that $R_0 = S_0 = P \mod A_0 = (P{-}A_0) \mod A_0$. 
Noting that $P{-}A_0 = \sum_{i=d+1}^n a_i X^i$, we obtain
$b_\varphi(P{-}A_0) \geq \kappa$ and then $b_\varphi(R_0) = b_\varphi(S_0)
\geq \kappa$. Finally observe that:
$$T_0 = (1 - B_0) \mod A_0 = \big((A_0 - P) \div A_0\big) \mod A_0.$$
Therefore $b_0(T_0) \geq \kappa$ results from $b_\varphi(A{-}P_0) \geq 
\kappa$ thanks to Lemma~\ref{lem:bphib0}. 
We have then established~\eqref{eq:induction} when $i = 0$.

We now assume~\eqref{eq:induction} for the index $i$.
From $A_{i+1} = A_i + R_i$ and the estimation $b_\varphi(R_i) \geq 2^i 
\kappa > 0$, we derive $\NF(A_{i+1}) = \varphi_{|[0,d]}$. Therefore,
Lemma~\ref{lem:bphib0} applies with $A = A_i$ and $A = A_{i+1}$.
Now using the definition of $B_{i+1}$, we get $b_0(B_{i+1}) \geq 0$.
As a consequence:
$$b_\varphi(R_i B_{i+1}) \geq b_\varphi(R_i) + b_0(B_{i+1})
\geq 2^i \kappa$$
by Lemma~\ref{lem:bphib0} and the induction hypothesis.
Using again Lemma~\ref{lem:bphib0}, we then derive from 
\eqref{eqdef:Biminus} and \eqref{eqdef:Siminus}, $b_0(\Delta B_i) \geq 
2^i \kappa$ and $b_\varphi(\Delta S_i) \geq 2^i \kappa$.
Similarly, using \eqref{eqdef:Si2} and the estimations we already know,
we obtain $b_\varphi(S_i) \geq 2^i \kappa$. Combining this with
$b_\varphi(\Delta S_i) \geq 2^i \kappa$, we find
$b_\varphi(S_{i+1}) \geq 2^i \kappa$ as well. Applying again and again
the same strategy, we deduce successively
$b_0(\Delta V_i) \geq 2^i \kappa$ using \eqref{eqdef:Viminus},
$b_0(1{-}Q_i) \geq 2^i \kappa$ using \eqref{eqdef:Qiminus},
$b_\varphi(R_{i+1}) \geq 2^{i+1} \kappa$ using \eqref{eq:Riplus},
and finally $b_0(T_{i+1}) \geq 2^{i+1} \kappa$
using \eqref{eq:ViBiplus}. The equalities and inequalities
of Eq.~\eqref{eq:induction} have then all been established for
the index $i+1$ and the induction goes.

@@

\begin{rem}
\label{rem:slope-factor}
It follows from the proof above that the conclusion of 
Theorem~\ref{theo:slope-factor} is still correct as soon as $A_0$ 
and $V_0$ satisfies:
$$b_\varphi\big(V_0 P \mod A_0\big) > 0
\quad \text{and} \quad
b_0\big((1 - V_0 B_0) \mod A_0\big) > 0$$
except that the constant $\kappa$ giving the rate of convergence
should be now defined as:
$$\kappa = \min \big( 
b_\varphi\big(V_0 P \mod A_0\big), \,
b_0\big((1 - V_0 B_0) \mod A_0\big)\big).$$
\end{rem}

@@

\begin{prop}
We keep all the above notations and assumptions. We set:
$$\delta = \min_{x \in [0,n{-}1]} \varphi_P(x) - \varphi(x)$$
and assume that $\delta > 0$. 
Then the factor $A^{(1)}$ is known with precision at least 
$O(\varphi_{A^{(1)}})$ with
$\varphi_{A^{(1)}} = \varphi_{|[0,d{-}1]} - \varphi(d) + \delta$.
\end{prop}

@@

@@

\noindent
{\bf Lattice precision.}
The precision datum is given here by a lattice $H_P$ in $K_{\leq n{-}1}
[X]$; we shall then write:
$$P = P_\app + O(H_P)$$
where $P_\app$ is a \emph{monic} approximation of the inexact polynomial 
$P$ we want to factor. We assume from now that $H_P$ is sufficiently 
small so that the Newton polygon of $P$ is well defined. We then can
define the function:
$$F : P_\app + H_P \to K_{=d}[X] \times K_{=n{-}d}[X]$$
mapping a polynomial $P$ to the couple $(A^{(1)}, B^{(1)})$ obtained
from it. We set $(A_\app^{(1)}, B_\app^{(1)}) = F(P_\app)$.

@@

\begin{prop}
\label{prop:precA1}
The application $P \mapsto A^{(1)}$ is of class $C^1$ on $P_\app + H_P$
and its differential at at some point $P$ is the linear mapping:
$$dP \mapsto dA^{(1)} = (V^{(1)} \: dP) \mod A^{(1)}$$
where $(A^{(1)}, B^{(1)}) = F(P)$ and $V^{(1)}$ is the inverse of 
$B^{(1)}$ modulo $A^{(1)}$.
\end{prop}

@@

>>>>

\todo{Write introduction.}

\noindent
{\bf Main Results.}

\noindent
{\bf Organization of the paper.}

@@

It is worth noting that tracking precision using this representation is 
rather easy. For example, if $x$ and $y$ are known with absolute (resp. 
relative) precision $N_x$ and $N_y$ respectively, one can compute the 
sum $x+y$ (resp. the product $xy$) at absolute (resp. relative) 
precision $\min(N_x,N_y)$. Computations with $p$-adic and Laurent
series are often handle this way on symbolic computation softwares.

@@

\begin{deftn}
A \emph{Newton function of degree $n$} is a convex function 
$\varphi : [0,n] \to \R \cup \{+\infty\}$ which is piecewise affine, 
which takes a finite value at $n$ and whose epigraph $\Epi(\varphi)$ 
have extremal points with integral abscissa.
\end{deftn}

@@

\todo{Add introduction.}
In the sequel, we use the notation $A \div B$ (resp $A \mod B$)
for the quotient (resp. the remainder) in the Euclidean division of $A$ 
by $B$.

@@

\noindent
{\bf Newton precision.}
We consider here the case where the precision is given by Newton
functions. Concretely, we pick $A, B \in K[X]$ two polynomials which 
are known at precision $O(\varphi_A)$ and $O(\varphi_B)$ respectively:
$$A = A_\app + O(\varphi_A)
\quad \text{and} \quad
B = B_\app + O(\varphi_B)$$
Here $A_\app$ and $B_\app$ are some approximations of $A$ and $B$ respectively 
and $\varphi_A$ and $\varphi_B$ denotes two Newton functions of degree 
$\deg A$ and $\deg B$ respectively.
We are interested in determining the precision on $A \mod B$ and $A
\div B$. The following proposition gives a theoretical answer under
mild assumptions.

@@

We observe several interesting properties. First of all, the gains for 
Newton precision and jagged precision always agree though one may have 
thought at first that Newton precision is weaker. Since performing
precision computations in the Newton framework is cheaper, it seems
(at least on this example) that using the jagged precision model is not
relevant.

@@

\begin{comment}
\subsubsection{Tristan's proof}

@@

\subsubsection{Xavier's proof}
\end{comment}

If $\lambda_0 = -\infty$ or $\lambda_1 = +\infty$, the sequence $(A_i)$
is constant and the theorem is obvious. We then assume that $\lambda_0$
and $\lambda_1$ are both finite.
We notice that, when the polynomial is changed into $cP$ where $c$ is a 
nonzero constant lying in a finite extension of $K$, the $A_i$'s are all 
multiplied by $c$ as well whereas the $B_i$'s and the $V_i$'s remained 
unchanged. Therefore, the theorem holds for $P$ if and only if it holds 
for $cP$. As a consequence we may assume that $P$ is normalized so that 
$\NF(P)(d) = d \lambda_0$. We define the function $\varphi : \R^+ \to \R 
\cup \{+\infty\}$ by:
\begin{equation}
\label{eqdef:functionphi}
\begin{array}{r@{\,\,}ll}
\varphi(x) & = \NP(P)(x) & \text{for } x \leq d \smallskip \\
& = \lambda_0 (x-d) + \NP(P)(d) & \text{for } x > d.
\end{array}
\end{equation}
For a polynomial $Q \in K[X]$ of degree $n$, we further define:
\begin{align}
b_\varphi(Q) & = \min_{x \in [0,n]} \NF(Q)(x) - \varphi(x) 
\label{eqdef:bphi} \\
\text{and} \quad
b_i(Q) & = \min_{x \in [0,n]} \NF(Q)(x) - \lambda_i x
\quad \text{for } i \in \{0,1\}.
\label{eqdef:b0}
\end{align}
Set also $b_\varphi(0) = b_0(0) = b_1(0) = +\infty$ by convention.
With the normalization of $P$ we chose above, we have $b_0(P)
= b_\varphi(P) = 0$ and $b_\varphi(Q) \leq b_0(Q)$ for all polynomial
$Q$. Similarly $b_1(Q) \leq b_0(Q)$ for all $Q$.

\begin{lem}
\label{lem:bphib0}
Let $b \in \{b_\varphi, b_0, b_1\}$. For $Q_1, Q_2 \in K[X]$:

@@

c) $b_\varphi(Q_1 Q_2) \geq b_\varphi(Q_1) + b_0(Q_2)$

@@

Let $t_1$ (resp. $t_2$) be the translation of vector $(0, b_\varphi
(Q_1))$ (resp. $(0, b_0(Q_2))$. It follows from the definition of
$b_\varphi$ that $\NP(Q_1)$ is a subset of $t_1(\Epi(\varphi))$ where
$\Epi(\varphi)$ denotes the epigraph of $\varphi$. Similarly $\NP(Q_2)
\subset t_2(C)$ where $C$ is the convex cone generated by the vectors 
starting from $(0,0)$ to $(0,1)$ and $(1, \lambda_0)$. Thus
$$\NP(Q_1 Q_2) \subset t_2 \circ t_1 \big(\Epi(\varphi) + C\big) =
t_2 \circ t_1\big(\Epi(\varphi)\big)$$
and \emph{c)} follows.

@@

We are now going to prove by induction on $i$ the conjonction of all
equalities and inequalities below:
\begin{equation}
\label{eq:induction}
\begin{array}{l}
\NF(A_i) = \varphi_{|[0,d]}, \smallskip \\
b_1(V_i) \geq 0, \quad
b_\varphi(R_i) \geq 2^i \kappa \smallskip \\
b_\varphi(S_i) \geq 0, \quad
b_0(T_i) \geq 2^i \kappa.
\end{array}
\end{equation}

Noting that $A_0$ and $P$ agree up to degree $d$ and that $\NP(P)$ has 
an extremal point at abscissa $d$, we get $\NF(A_0) = \varphi_{|[0,d]}$.
Clearly $b_1(V_0) \geq 0$ since $V_0 = 1$. It follows from the 
definitions that $R_0 = S_0 = P \mod A_0 = (P{-}A_0) \mod A_0$. 
Noting that $P{-}A_0 = \sum_{i=d+1}^n a_i X^i$, we obtain
$b_\varphi(P{-}A_0) \geq \kappa$ and then $b_\varphi(R_0) = b_\varphi(S_0)
\geq \kappa$. Finally observe that:
$$T_0 = (1 - B_0) \mod A_0 = \big((A_0 - P) \div A_0\big) \mod A_0.$$
Therefore $b_0(T_0) \geq \kappa$ results from $b_\varphi(A{-}P_0) \geq 
\kappa$ thanks to Lemma~\ref{lem:bphib0}. 
We have then established~\eqref{eq:induction} when $i = 0$.

We now assume~\eqref{eq:induction} for the index $i$.
From $A_{i+1} = A_i + R_i$ and the estimation $b_\varphi(R_i) \geq 2^i 
\kappa > 0$, we derive $\NF(A_{i+1}) = \varphi_{|[0,d]}$. Therefore,
Lemma~\ref{lem:bphib0} applies with $A = A_i$ and $A = A_{i+1}$.
Now coming back to the the definition of $B_{i+1}$ and using
Theorem~\ref{theo:EDivisionNP}, we get $b_0(B_{i+1}) \geq b_1(B_{i+1}) 
\geq 0$. As a consequence:
$$b_\varphi(R_i B_{i+1}) \geq b_\varphi(R_i) + b_0(B_{i+1})
\geq 2^i \kappa$$
by Lemma~\ref{lem:bphib0} and the induction hypothesis.
Using again Lemma~\ref{lem:bphib0}, we then derive from 
\eqref{eqdef:Biminus} and \eqref{eqdef:Siminus}, $b_0(\Delta B_i) \geq 
2^i \kappa$ and $b_\varphi(\Delta S_i) \geq 2^i \kappa$.
Similarly, using \eqref{eqdef:Si2} and the estimations we already know,
we obtain $b_\varphi(S_i) \geq 2^i \kappa$. Combining this with
$b_\varphi(\Delta S_i) \geq 2^i \kappa$, we find
$b_\varphi(S_{i+1}) \geq 2^i \kappa$ as well. Applying again and again
the same strategy, we deduce successively
$b_0(\Delta V_i) \geq 2^i \kappa$ using~\eqref{eqdef:Viminus},
$b_0(1{-}Q_i) \geq 2^i \kappa$ using~\eqref{eqdef:Qiminus},
$b_\varphi(R_{i+1}) \geq 2^{i+1} \kappa$ using~\eqref{eq:Riplus},
and then $b_0(T_{i+1}) \geq 2^{i+1} \kappa$
using~\eqref{eq:ViBiplus}. Finally, coming back to the recurrence
defining $V_{i+1}$ and remembering that $b_1(V_i)$ and $b_1(B_{i+1})$
are both nonnegative, we find $b_1(V_{i+1}) \geq 0$.
The equalities and inequalities
of Eq.~\eqref{eq:induction} have then all been established for
the index $i+1$ and the induction goes.

@@

\begin{rem}
\label{rem:slope-factor}
It follows from the proof above that the sequence $(V_i)_{i \geq 0}$
converges as well. Its limit $V_\infty$ is an inverse of $B_\infty
= P \div A_\infty$ modulo $A_\infty$ and it satisfies in addition
$b_1(V_\infty) \geq 0$.

Moreover, the conclusion of 
Theorem~\ref{theo:slope-factor} is still correct if $A_0$ is any 
polynomial of degree $d$ and leading coefficient $a_d$ and $V_0$
is any polynomial as soon as they satisfy:
$$b_\varphi\big(V_0 P \mod A_0\big) > 0
\quad \text{and} \quad
b_0\big((1 - V_0 B_0) \mod A_0\big) > 0$$
except that the constant $\kappa$ giving the rate of convergence
should be now defined as:
$$\kappa = \min \big( 
b_\varphi\big(V_0 P \mod A_0\big), \,
b_0\big((1 - V_0 B_0) \mod A_0\big)\big).$$
\end{rem}

@@

\begin{prop}
\label{prop:Newtonprecslope}
We keep all the above notations and assumptions. We set:
$$\delta = \min_{x \in [0,n{-}1]} \varphi_P(x) - \varphi(x)$$
and assume that $\delta > 0$. 
Then the factor $A^{(1)}$ is known with precision at least 
$O(\varphi_{A^{(1)}})$ with
$\varphi_{A^{(1)}} = \varphi_{|[0,d{-}1]} - \varphi(d) + \delta$.
\end{prop}

@@

\begin{rem}
Under the hypothesis~\textbf{(H)} introduced below, a correct precision 
on $A^{(1)}$ is also $O(\psi_{A^{(1)}})$ where:
$$\psi_{A^{(1)}} = \big(\varphi_P \nftimes \big(\NF(V_\app)
- \NF(P)(d)\big)\big) \nfmod \NF(P)_{|[0,d]}.$$
This follows from Proposition~\ref{prop:precA1} using
$V^{(1)}_\app = a_d^{-1} V_\app$. It follows in addition from 
Remark~\ref{rem:slope-factor} that $\NF(V_\app)$ is bounded from below 
by $x \mapsto \lambda_1 x$. This yields the bound
$\psi_{A^{(1)}} \geq \big(\varphi_P \nftimes \psi\big) \nfmod 
\NF(P)_{|[0,d]}$
where $\psi : [0,d{-}1] \to \R$ is the affine function mapping $x$
to $\lambda_1 x - \NF(P)(d)$. 
\end{rem}

@@

\noindent
{\bf Lattice precision.}
The precision datum is given here by a lattice $H_P$ in $K_{\leq n{-}1}
[X]$; we shall then write:
$$P = P_\app + O(H_P)$$
where $P_\app$ is a \emph{monic} approximation of the inexact polynomial 
$P$ we want to factor. We assume from now that $H_P$ is sufficiently 
small so that the Newton polygon of $P$ is well defined. We then can
define the function:
$$F = (F_A, F_B) : P_\app + H_P \to K_{=d}[X] \times K_{=n{-}d}[X]$$
mapping a polynomial $P$ to the couple $(A^{(1)}, B^{(1)})$ obtained
from it. We set $(A_\app^{(1)}, B_\app^{(1)}) = F(P_\app)$.

@@

\begin{prop}
\label{prop:precA1}
The application $F_A : P \mapsto A^{(1)}$ is of class $C^1$ on $P_\app + H_P$
and its differential at at some point $P$ is the linear mapping:
$$dP \mapsto dA^{(1)} = (V^{(1)} \: dP) \mod A^{(1)}$$
where $(A^{(1)}, B^{(1)}) = F(P)$ and $V^{(1)}$ is the inverse of 
$B^{(1)}$ modulo $A^{(1)}$.
\end{prop}

@@

A remarkable Corollary of Proposition~\ref{prop:precA1} asserts the
optimality of Proposition~\ref{prop:Newtonprecslope} in a particular 
case.

\begin{cor}
We assume~\textbf{(H)}.
When the precision of $P$ is given by $O(\varphi_P)$ with:
$$\varphi_P = (\NF(P) + \delta)_{|[0,d-1]}
\quad \text{where $\delta \in \R$}$$
the precision of $A^{(1)}$ given by 
Proposition~\ref{prop:Newtonprecslope} is optimal.
\end{cor}

\begin{proof}
First remark that the $\delta$ defined in the statement of 
Proposition~\ref{prop:Newtonprecslope} coincide with the $\delta$
introduced in the Corollary. Define
$\varphi_{A^{(1)}} = \varphi_{|[0,d{-}1]} - \varphi(d) + \delta$.
Let $H_P$ (resp. $H_{A^{(1)}})$ be the lattice consisting of
polynomials of degree at most $n{-}1$ (resp. at most $d{-}1$)
whose Newton function is not less that $\varphi_P$ (resp. 
$\varphi_{A^{(1)}}$). We have to show that $F'_A(P_\app)(H_P) = 
H_{A^{(1)}}$. But, according to Proposition~\ref{prop:precA1}
the mapping $G : K_{\leq d{-}1}[X] \to K_{\leq n{-}1}[X]$,
$$dA^{(1)} \mapsto (B_\app^{(1)} \: dA^{(1)}) \mod A_\app^{(1)}$$
is a right inverse of $F'_A(P_\app)$. It is then enough to prove
that $G$ takes $H_{A^{(1)}}$ to $H_P$, which can be done easily
using Theorem~\ref{theo:EDivisionNP}.
\end{proof}
